---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# isonoi

<!-- badges: start -->
[![R-CMD-check](https://github.com/isonoi/isonoi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/isonoi/isonoi/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of isonoi is to provide example data and functions to demonstrate the concept of 'iso voronoi' polygons.

It is designed to be a prototype implementation of ideas outlined and demonstrated with example data and reproducible code in https://github.com/isonoi/isonoi

Give it a spin with the reproducible examples shown below.

```{r, eval=FALSE}
remotes::install_github("isonoi/isonoi")
```

```{r inputs}
# TODO: remove this and keep only library call
devtools::load_all()
# library(isonoi)
library(sf)
x = net_oldenburg_raw
points = points_oldenburg
grid = iso_grid(x)
plot(grid, border = "grey")
plot(sf::st_geometry(x), add = TRUE)
plot(points, col = "red", add = TRUE, pch = 18, cex = 2)
```

The 3 figures below show outputs from the packages next to the standard voronoi diagram.

```{r outputs}
library(tmap)
vnoi = iso_vnoi(x) # TODO
vgrid = iso_vgrid(points, grid)
# plot(vgrid[19, ])
m2 = tm_shape(vgrid) + tm_fill("name")
# m3 = iso_osrm(x) # TODO
tmap_arrange(m2, m2, m2, nrow = 1)
```

