---
title: "Isonoi - Calculate voronoi-style polygons based on route distances / durations"
runningtitle: "Isonoi"
output: rmarkdown::html_vignette
author:
   - name: Robin Lovelace
     affiliation: Institute for Transport Studies and Leeds Institute for Data Analytics, University of Leeds, UK
   - name: Bernhard C. Dannemann
     affiliation: Chair of Applied Macroeconomics, University of Oldenburg, DEU
vignette: >
  %\VignetteIndexEntry{Isonoi - Calculate voronoi-style polygons based on route distances / durations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
pkgdown:
  as_is: true
  set_null_theme: false
keywords: "isochrones, voronoi polygons, tesselation, modifiable area unit problem"
bibliography: references.bib
# csl: josis.csl
abstract: |
  We calculate voronoi-style polygons based on route distances / durations using
  Openstreetmap road network data.
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(isonoi)
```


# Introduction

- In urban planning, voronoi polygons are employed, for example, for assessing freight loading zones [@su11051276]



# Partitioning the plane into isochrones

- Conceptual differences:
  - Voronoi uses a distance metric (usually L2 or L1), which is not available for road networks (routing engine as a *black box*)
  - While voronoi polygons extend into *empty space*, isochrones form a convex hull around points that can be reached, given a time constraint, within the road network

# Applications
- Accessibility maps of hospitals
- Market regions of firms
- Transport planning
- Catchment areas of pubs 
- For city centers: Isonoi vs. clockboard zones!

# Discussion and Conclusion

# References
